results

### 2020-08-23 analysis/results.Rmd
fix table

---
bibliography: references.bib
csl: chicago.csl
output: github_document
always_allow_html: true
---

@@

```{r}
# required data spreadsheets
# pub volume
els_pub_volume <- readr::read_csv(
  here::here("data", "article_volume_para.csv")
  ) 
# eligble journals 
eligible_jns <- hybrid_df %>% 
  filter(oa_archive == FALSE) %>% 
  distinct(issn)
# pub volume eligble data
els_yr <- els_pub_volume %>%
  filter(issn %in% eligible_jns$issn) %>%
  group_by(issued_year) %>%
  summarise(journals = n_distinct(issn),
            articles_n = sum(articles),
            articles_mean = mean(articles),
            articles_sd = sd(articles))

# oa
oa_per_jn_year <- hybrid_df %>%
  filter(oa_archive == FALSE) %>%
  group_by(issued_year, issn) %>%
  summarise(oa = n()) %>%
  ungroup()
oa_ind <- oa_per_jn_year %>%
  group_by(issued_year) %>%
  summarise(oa_n = sum(oa),
            oa_mean = mean(oa),
            oa_sd = sd(oa)) 
# oa uptake 
oa_uptake_ind <- els_pub_volume %>%
  filter(issn %in% eligible_jns$issn) %>%
  inner_join(oa_per_jn_year, by = c("issn", "issued_year")) %>%
  mutate(prop = oa / articles) %>%
  group_by(issued_year) %>%
  summarise(oa_uptake_mean = mean(prop),
            oa_uptake_sd = sd(prop))
# oa uptake all 
oa_uptake_15_19 <- els_pub_volume %>%
    filter(issn %in% eligible_jns$issn) %>%
    inner_join(oa_per_jn_year, by = c("issn", "issued_year")) %>%
    group_by(issn) %>%
    summarise(oa = sum(oa),
              articles = sum(articles)) %>%
    mutate(prop = oa / articles)

# all 
total_df <- tibble::tibble(
  issued_year = "2015-19",
  journals = hybrid_df %>% filter(oa_archive == FALSE) %>% distinct(issn) %>% nrow(),
  articles_n = els_pub_volume %>% filter(issn %in% eligible_jns$issn) %>% pull(articles) %>% sum(),
  articles_mean = els_pub_volume %>% filter(issn %in% eligible_jns$issn) %>% group_by(issn) %>% summarise(n = sum(articles)) %>% pull(n) %>% mean(),
  articles_sd = els_pub_volume %>% filter(issn %in% eligible_jns$issn) %>% group_by(issn) %>% summarise(n = sum(articles)) %>% pull(n) %>% sd(),
  oa_n = hybrid_df %>% filter(oa_archive == FALSE) %>% nrow(),
  oa_mean = hybrid_df %>% filter(oa_archive == FALSE) %>% group_by(issn) %>% summarise(oa = n()) %>% pull(oa) %>% mean(),
  oa_sd = hybrid_df %>% filter(oa_archive == FALSE) %>% group_by(issn) %>% summarise(oa = n()) %>% pull(oa) %>% sd(),
  oa_uptake = oa_n / articles_n,
  oa_uptake_mean = mean(oa_uptake_15_19$prop),
  oa_uptake_sd = sd(oa_uptake_15_19$prop)
         )

@@

```{r}
table_descriptives_ind <- tribble(
  ~ind_group, ~ind, ~ind_name,
  "Hybrid Journals with OA articles", "Total", "Total",
  "Publication Volume", "articles_n", "Articles",
  "Publication Volume", "articles_mean", "Mean",
  "Publication Volume", "articles_sd", "SD",
  "OA Volume", "oa_n", "Total",
  "OA Volume", "oa_mean", "Mean",
  "OA Volume", "oa_sd", "SD",
  "OA Uptake", "oa_uptake", "Overall OA Uptake",
  "OA Uptake", "oa_uptake_mean", "Mean",
  "OA Uptake", "oa_uptake_sd", "SD",
)
inner_join(table_descriptives_ind, ind_summary_table, by = c("ind" = "indicator")) %>%
  dplyr::select(-ind) %>%
  gt(rowname_col = "ind_name", groupname_col = "ind_group") %>%
  fmt_number(contains("20")) %>%
  fmt_number(contains("20"), 
             rows = c("Articles", "Total"),
             decimals = 0) %>%
  tab_style(cell_text(weight = "bold"),
            locations = cells_row_groups()
  )
```

>>>>

---
bibliography: references.bib
csl: chicago.csl
output: html_document
always_allow_html: true
---

@@

```{r}
# required data spreadsheets
# pub volume
els_pub_volume <- readr::read_csv(
  here::here("data", "article_volume_para.csv")
  ) 
# eligble journals 
eligible_jns <- hybrid_df %>% 
  filter(oa_archive == FALSE) %>% 
  distinct(issn)
# pub volume eligble data
hybrid_volume <- els_pub_volume %>%
  filter(issn %in% eligible_jns$issn) %>%
  inner_join(hybrid_df, by = c("issn", "issued_year")) %>%
  filter(oa_archive == FALSE)

els_articles <- 
  hybrid_volume %>%
  distinct(issued_year, issn, articles) %>%
  group_by(issued_year) %>%
  summarise(
    articles_n = sum(articles),
            articles_mean = mean(articles),
            articles_sd = sd(articles)
    )
els_yr <- 
  hybrid_volume %>%
  group_by(issued_year) %>%
  summarise(journals = n_distinct(issn)) %>%
  inner_join(els_articles, by = "issued_year")

# oa
oa_per_jn_year <- hybrid_volume %>%
  group_by(issued_year, issn) %>%
  summarise(oa = n(), .groups = "drop")
oa_ind <- oa_per_jn_year %>%
  group_by(issued_year) %>%
  summarise(oa_n = sum(oa),
            oa_mean = mean(oa),
            oa_sd = sd(oa)) 
# oa uptake 
oa_uptake_ind <- hybrid_volume %>% 
  distinct(issued_year, issn, articles) %>%
  inner_join(oa_per_jn_year, by = c("issn", "issued_year")) %>%
  mutate(prop = oa / articles) %>%
  group_by(issued_year) %>%
  summarise(oa_uptake_mean = mean(prop),
            oa_uptake_sd = sd(prop))
# oa uptake all 
oa_uptake_15_19 <- hybrid_volume %>% 
  distinct(issued_year, issn, articles) %>%
  inner_join(oa_per_jn_year, by = c("issn", "issued_year")) %>%
    group_by(issn) %>%
    summarise(oa = sum(oa),
              articles = sum(articles)) %>%
    mutate(prop = oa / articles)

# all 
total_df <- tibble::tibble(
  issued_year = "2015-19",
  journals = hybrid_volume %>% distinct(issn) %>% nrow(),
  articles_n = hybrid_volume %>% distinct(issn, articles, issued_year) %>% pull(articles) %>% sum(),
  articles_mean = hybrid_volume %>% distinct(issn, articles, issued_year) %>% pull(articles) %>% mean(),
  articles_sd = hybrid_volume %>% distinct(issn, articles, issued_year) %>% pull(articles) %>% sd(),
  oa_n = nrow(hybrid_volume),
  oa_mean = hybrid_volume %>% group_by(issn) %>% summarise(oa = n()) %>% pull(oa) %>% mean(),
  oa_sd = hybrid_volume %>% group_by(issn) %>% summarise(oa = n()) %>% pull(oa) %>% sd(),
  oa_uptake = oa_n / articles_n,
  oa_uptake_mean = mean(oa_uptake_15_19$prop),
  oa_uptake_sd = sd(oa_uptake_15_19$prop)
         )

@@

```{r}
table_descriptives_ind <- tribble(
  ~ind_group, ~ind, ~ind_name,
  "Hybrid Journals with OA articles", "journals", "Journals",
  "Publication Volume", "articles_n", "Articles",
  "Publication Volume", "articles_mean", "Mean",
  "Publication Volume", "articles_sd", "SD",
  "OA Volume", "oa_n", "OA Articles",
  "OA Volume", "oa_mean", "Mean per Journal",
  "OA Volume", "oa_sd", "SD",
  "OA Uptake (in%)", "oa_uptake", "OA Percentage",
  "OA Uptake (in%)", "oa_uptake_mean", "Mean per Journal",
  "OA Uptake (in%)", "oa_uptake_sd", "SD"
)
inner_join(table_descriptives_ind, ind_summary_table, by = c("ind" = "indicator")) %>%
  dplyr::select(-ind) %>%
  gt(rowname_col = "ind_name", groupname_col = "ind_group") %>%
  fmt_number(contains("20"), decimals = 2) %>%
  fmt_number(contains("20"), 
             rows = c("Journals", "Articles", "OA Articles"),
             decimals = 0) %>%
  tab_style(cell_text(weight = "bold"),
            locations = cells_row_groups()
  )
```
